---
title: "assessment1.1"
author: "Melody GENG s4660143"
date: "12/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
PART 1

#**Rmarkdown editing**
**R Markdown is a file format for making dynamic documents with R.**

#insert data
```{r}
fastfood<-read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')

fastfood<-readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

```

#**apply library**
```{r}
install.packages("tidyverse")
install.packages("skimr")
install.packages("janitor")
install.packages("dplyr")
install.packages("reshape")
install.packages("tidyr")

library(tidyverse)
library(skimr)
library(janitor)
library(dplyr)
library(reshape)
library(tidyr)
```
###6.
```{r}
fastfood <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
data%>%head(10)
```

###7. Display the first 10 rows of the dataset.and the first 5 variables**
```{r}
data%>%head (10)
data<-5
data_text<-"5"
fastfood<-readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
knitr::kable(head(fastfood[,1:5]),"pipe")

```

###8.Display the observations that has more than 1000 calories**
```{r}
fastfood%>%
  filter(calories>1000)
```

###9.Observations with more than 40 in total_fat and more than 80 in total_carb in a new variable (dataset) called `dont_eat_this`
```{r}
dont_eat_this<-fastfood%>%
select(restaurant,item,total_carb)%>%
  filter(total_fat>40)%>%
  filter(total_carb>80)
```
```{r}
fastfood%>%
  filter(total_fat>40)
filter(total_carb>80)%>%
  select(restarant,item,total_fat, total_carb)

```

###10.Display observations from restaurant Mcdonalds
```{r}
fastfood%>%
  filter(restaurant--"Mcdonalds")
```

PART 2

install.packages(broom)
library(broom)

theme_set(theme_bw())

###11.Display the types of variables in the dataset using `skimr` package 
```{r}
data <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv"
fastfood_calories <- read_tsv(fastfood_data)
```
###12.the count of observations for each restaurant
```{r}
fastfood %>%
  count(restaurant)
```
###13.(group_by()), summaries and display the average number of calories for each restaurant.
```{r}
fastfood %>%
  group_by(restaurant,calories)
  summarize(calories=sum(restaurant,calories))
```
###14.Add a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories`
```{r}
average_calories<-fastfood %>%
  group_by(restaurant) %>%
  mutate(average_calories=mean(calories)) %>% ungroup()
glimpse(average_calories) %>% select(restaurant, average_calories)
fastfood<-fastfood %>%
  group_by(restraurant) %>%
  mutate(average_calories=mean(calories)) %>% ungroup()
glimpse(fastfood) %>% select (restaurant, average_calories)
```
###15.Display the data vis of total fat per each type of restaurant.
```{r}
fastfood %>%
  select(total_fat, restaurant)
```
This form of data display allows you to see the difference in data more intuitively. It is easier for people to find the numbers they want from different restaurants and different calorie data.

###16.Add a variable to the data set, which calculates the maximum total fat per type of restaurant and call it `max_total_fat` 
```{r}
max_total_fat<-fastfood %>%
  group_by( restaurant) %>%
  mutate(max_total_fat=maximum(total_fat)) %>% ungroup()
```
###17.Use observations for McDonald to plot sugar variable against protein with `geom_point()` 
```{r}
ggplot(fastfood,
       aes(sugur,protein))+
  geom_point()
```
Part 3

###18.Identify variable(s) which should be factors and transform their type into a factor variable.
```{r}
fastfood%>%
  mutate_if(is.character, factor)
```
###19
```{r}
fastfood %>%
  mutate(calories_type= cut_number(calories, n=3,labels=c("low", "med","high"))
```
###20
```{r}
ggplot(calories_type, aes(calories, calories_type,))+
  geom_col()+
  theme_light()+
  labs(x="Restaruant", y="Calories Types", title = "Data", caption = "Image: type")
```
###21
```{r}
trans_fat_percentage<-calories_type %>%
  group_by(restaurant) %>%
  mutate(trans_fat_percentage= trans_fat_percentage * 10)
```
###22
```{r}
ggplot(trans_fat_percentage,
       aes(total_fat,trans_fat_percentage))+
  geom_col()+
  theme_dark()+
  labs(x="Resraurant", y="Trans Fat percentage", title = "Data visualisation", caption = "Image: Trans Fat Percentage")
```
###23
```{r}
trans_fat_percentage%>%
  group_by(restaurant)%>%
  summarise(mean_total_fat=mean(total_fat))
```
###24
```{r}
trans_fat_percentage %>%
  group_by(restaurant) %>%
  ungroup()%>%
  mutate(restaurant=fct_reorder(restaurant, average_total_fat)) %>%
  ggplot(aes(restaurant, average_total_fat))+
  geom_col()+
  facet_wrap(restaurant)
labs(x="Name of restaurant", y="Average Total Fat", title="Data visualisation", capital="Image:Bar Graph")+
  theme_light()
```






  
